Optimal management of a stochastically varying population when policy adjustment is costly

### 2015-05-08 manuscripts/manuscript.Rmd
working on revisions

ggplot(fees, aes(c2, (npv0-value)/npv0, lty=variable, color=variable)) + 
  geom_line() + 
  geom_hline(aes(yintercept=reduction), linetype=4) + 
  xlab("Penalty coefficient") +
  ylab("Reduction in net present value") + 
  scale_linetype_discrete(labels=relabel, breaks = c('L1', 'L2', 'fixed'), name = 'cost model') + 
  scale_color_discrete(labels=relabel, breaks = c('L1', 'L2', 'fixed'), name = 'cost model') + 
  annotate("text", mean(c2), reduction+.01, label = "Calibration for 25% reduction in NPV")
 # rename scale from 'variable' to 'adjustment cost for policy:'

@@

@@

ggplot(filter(table1_long, reduction == 0.25),
  aes(penalty.fn, value, fill = variable)) + 
  geom_bar(stat="identity", position="dodge") + 
  scale_fill_discrete(name="error type") + 
  scale_x_discrete(labels = c('L1' = substitute(paste(Pi[1])),
                              'L2' = substitute(paste(Pi[2])),
                              'fixed' = substitute(paste(Pi[3])))) + 
  xlab("Cost model") + 
  ylab(expression(NPV[0])) + theme_tufte(base_size=16)
write.csv(table1_long, "components/data/figure6.csv")
```

>>>>

ggplot(fees, aes(c2, (npv0-value)/npv0, lty=variable, color=variable)) + 
  geom_line() + 
  geom_hline(aes(yintercept=reduction), linetype=4) + 
  xlab("Penalty coefficient") +
  ylab("Reduction in net present value") + 
  scale_linetype_discrete(labels=relabel, breaks = c('L1', 'L2', 'fixed'), name = 'cost model') + 
  scale_color_discrete(labels=relabel, breaks = c('L1', 'L2', 'fixed'), name = 'cost model') + 
  annotate("text", mean(c2), reduction+.02, label = "25% reduction in NPV")

@@

f4df$penalty_fn <- factor(f4df$penalty_fn, levels = c("L1", "L2", "fixed"))

@@

table1_long$penalty.fn <- factor(table1_long$penalty.fn, levels = c("L1", "L2", "fixed"))

ggplot(filter(table1_long, reduction == 0.25),
  aes(penalty.fn, value, fill = variable)) + 
  geom_bar(stat="identity", position="dodge") + 
  scale_fill_discrete(name="error type") + 
  scale_x_discrete(labels = c('L1' = substitute(paste(Pi[1])),
                              'L2' = substitute(paste(Pi[2])),
                              'fixed' = substitute(paste(Pi[3])))) + 
  xlab("Cost model") + 
  ylab(expression(NPV[0])) 
write.csv(table1_long, "components/data/figure6.csv")
```
